Diel activity GAMs

### 2021-10-22 README.Rmd
fieldwork photo
rearrange
unimelb

Funding and support for these surveys came from the Conservation Ecology Centre, the Victorian  Government Department of Environment, Land, Water, and Planning, Parks Victoria, Arthur Rylah  Institute for Environmental Research, Parks Victoria.

@@

>>>>

Funding and support for these surveys came from the University of Melbourne, Conservation Ecology Centre, the Victorian  Government Department of Environment, Land, Water, and Planning, Parks Victoria, Arthur Rylah  Institute for Environmental Research, Parks Victoria.

@@

```{r photo, echo = FALSE}
knitr::include_graphics("figs/steph.jpg")
```
